\documentclass[mat2, anglescina, tisk]{fmfdelo-mod}
% \documentclass[fin2, anglescina, tisk]{fmfdelo}
% \documentclass[isrm2, anglescina, tisk]{fmfdelo}
% \documentclass[ped, anglescina, tisk]{fmfdelo}
% Če pobrišete možnost tisk, bodo povezave obarvane,
% na začetku pa ne bo praznih strani po naslovu, …

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% METAPODATKI
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% - vaše ime
\avtor{Izak Jenko}

% - naslov dela v slovenščini
\naslov{K3 ploskve z vidika izpeljanih kategorij}

% - naslov dela v angleščini
\title{K3 surfaces from a derived categorical viewpoint}

% - ime mentorja/mentorice s polnim nazivom:
%   - doc.~dr.~Ime Priimek
%   - izr.~prof.~dr.~Ime Priimek
%   - prof.~dr.~Ime Priimek
%   za druge variante uporabite ustrezne ukaze
\mentor{doc.~dr.~Matej Filip}
\somentor{dr.~Reinder Meinsma}
% \mentorica{...}
% \somentorica{...}
% \mentorja{...}{...}
% \somentorja{...}{...}
% \mentorici{...}{...}
% \somentorici{...}{...}
% mentorja morate navesti še z angleškim nazivom:
% - doc.~dr. = Assist.~Prof.~Dr.
% - izr.~prof.~dr. = Assoc.~Prof.~Dr.
% - prof.~dr. = Prof.~Dr.
\supervisor{Assist.~Prof.~Dr.~Matej Filip}
% \supervisor{...}
\cosupervisor{Dr.~Reinder Meinsma}
% \supervisors{...}{...}
% \cosupervisors{...}{...}

% - leto magisterija
\letnica{2025}

% - povzetek v slovenščini
%   V povzetku na kratko opišite vsebinske rezultate dela. Sem ne sodi razlaga
%   organizacije dela, torej v katerem razdelku je kaj, pač pa le opis vsebine.
\povzetek{
    Konstruiramo izpeljano kategorijo abelove kategorije, jo opremimo s strukturo triangulirane kategorije in definiramo izpeljane funktorje. Posebej se posvetimo omejeni izpeljani kategoriji koherentnih snopov na gladki projektivni raznoterosti in vpeljemo izpeljane funktorje, ki izhajajo iz geometrije. Preko njih definiramo in obravnavamo Fourier--Mukaijeve transformacije, najprej v okviru omejenih izpeljanih kategorij, nato na ravni $K$-grup in nazadnje na ravni racionalne kohomologije. Zatem se osredotočimo na kompleksne K3 ploskve in opišemo nekaj njihovih invariant, še zlasti presečno formo in Hodgevo strukturo. Nazadnje predstavimo Orlovov dokaz izpeljanega Torellijevega izreka, ki karakterizira izpeljano ekvivalentne K3 ploskve preko Mukaijevih mrež in pridruženih prostorov modulov stabilnih snopov.
}

% - povzetek v angleščini
\abstract{
    We construct the derived category of an abelian category, equip it with a triangulated structure and define derived functors. In particular we address the bounded derived category of coherent sheaves on a smooth projective variety and introduce derived functors of geometric origin. Utilizing them we define and study Fourier--Mukai transforms first at the level of derived categories, then at the level of $K$-groups and lastly at the level of rational cohomology. Focusing on complex K3 surfaces we describe some of their invariants, most notably their intersection form and associated Hodge structure. Lastly we present Orlov's proof of the derived Torelli theorem, which characterizes derived equivalent K3 surfaces in terms of their Mukai lattices and the associated moduli spaces of stable sheaves. 

    % The aim of this thesis is to develop the necessary 
    % We cover triangulated categories and categories of complexes. We define the derived category of an abelian category. 

}

% - klasifikacijske oznake, ločene z vejicami
%   Oznake, ki opisujejo področje dela, so dostopne na strani https://www.ams.org/msc/
\klasifikacija{14F08, 14J28, 18G80}

% - ključne besede, ki nastopajo v delu, ločene s \sep
\kljucnebesede{triangulirana kategorija\sep izpeljana kategorija\sep Fourier--Mukaijeva transformacija\sep K3 ploskev\sep izpeljani Torellijev izrek}

% - angleški prevod ključnih besed
\keywords{triangulated category, derived category\sep Fourier--Mukai transform\sep K3 surface, derived Torelli theorem}

% - neobvezna zahvala
\zahvala{
    I wish to thank Reinder Meinsma for his willingness to jump in on this project and share his enthusiasm for K3 surfaces with me over the past half year. Despite our meetings happening online, I very much enjoyed our weekly discussions, which filled me with motivation and a sense of camaraderie. I am grateful for your guidance throughout this process, from which I have learned a lot. 
    
    I am also very grateful to Matej Filip for expressing his interest in my work, thorough reading of the thesis and many helpful comments.

    I wish to extend my gratitude to Špela Špenko, who first introduced me to this part of algebraic geometry and later also provided the opportunity for me to participate in a summer school on non-commutative algebraic geometry in Antwerpen. This experience had a significantly positive impact on me and fostered my interest of further pursuing these topics. 
    
    I am thankful to the department of mathematics at FMF for passing on their knowledge, which I now deeply value. 

    I wish to thank my friends for expanding my horizons both within and beyond mathematics, and to all who have kindly looked after me during the process of writing this thesis. 

    Beyond all, I am grateful to my parents for their ever-present heartfelt support throughout all aspects of my journey.
    % , without whom this would not have been possible. 
}

% - ime datoteke z viri (vključno s končnico .bib), če uporabljate BibTeX
\literatura{references.bib}

% - ime datoteke z razširjenim povzetkom v slovenskem jeziku
\razsirjenipovzetek{razsirjenipovzetek.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% DODATNE DEFINICIJE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{macros.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ZAČETEK VSEBINE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\input{content/0-introduction.tex}
\newpage

\input{content/0-categorical-prerequisites.tex}
\newpage

\input{content/1-derived-categories.tex}
\newpage

\input{content/2-derived-categories-in-ag.tex}
\newpage

\input{content/3-Fourier-Mukai-transforms.tex}
\newpage

\input{content/4-K3-surfaces.tex}
\newpage

\input{content/5-Derived-Torelli.tex}
\newpage

\appendix
\input{chapters/spectral-sequences.tex}
\input{content/B-Lattice-theory.tex}

\end{document}